Supplementary Content

### 2022-02-20 experiments/2_supplement/supplement.Rmd
working on supplement
and other things

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE)
```

@@

In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state). The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).Stable states found with the replication method. Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

@@

Same as for the previous graph.

```{r temp_meth1, echo=FALSE, eval = TRUE}
plot_ss_result3(temp_meth, 1)
```

@@

```{r both_meth1, echo=FALSE, eval = TRUE}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

```{r echo = FALSE, eval = TRUE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

@@

```{r echo = FALSE, eval = TRUE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

@@

The figure above shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.

@@

*Review what the wait time is.*

Wait times of 1e6 hours produce the following results (same as those presented in the main report).

```{r wait_time_1e6, eval = TRUE}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

@@

```{r wait_time_1e5, eval = TRUE}

@@

```{r wait_time_1e4, eval = TRUE}

@@

```{r wait_time_1e3, eval = TRUE}

wait_time <- 1e3
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

```{r wait_time_1e2, eval = TRUE}

@@

Wait times of 1e5 produce the following results, which qualitatively and often quantitatively very similar to those for wait times of 1e6. There is a notable difference when there is variation in only SB, or CB-SB variation treatments with two or three strains:

Here, moderate increases in diversity have the same effect as with wait times of 1e6. However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition. Here is an example of the stable states when diversity is moderate:

```{r eval = TRUE}
wait_time <- "1e+04"
ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

only_SB_variable <- ss_3s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(PB_var_gmax_s) < 0.0001
  )
only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]

only_SB_variable$SB_var_gmax_s
```

```{r eval = TRUE}
fig_state_vs_o2diff(only_SB_variable[13,])
```

Increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift. When there is just a little more diversity in the SB, this happens:

```{r eval = TRUE}
fig_state_vs_o2diff(only_SB_variable[14,])
```

@@

### Example of transient dynamics at 1'000'000 hours

```{r echo = FALSE, fig.height=10}

single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
# sort(unique(ss_9s$CB_var_gmax_s))
# sort(unique(ss_9s$SB_var_gmax_s))
# ss_result <- ss_9s %>%
#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)

temp <- single_1e6 %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 1

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
#p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
```

```{r echo = FALSE, fig.height=10, eval = TRUE}

single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
# sort(unique(ss_9s$CB_var_gmax_s))
# sort(unique(ss_9s$SB_var_gmax_s))
# ss_result <- ss_9s %>%
#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)

temp <- single_2e6 %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 1

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
#p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
```

>>>>

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = TRUE)
```

@@

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/data/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state). The dashed up line refers to when their initial abundnace is low (favouring the anoxic state). Stable states found with the replication method. Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.

(ref:repl-meth2) Figure caption.

```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

@@

(ref:temp-meth2) ...

```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
plot_ss_result3(temp_meth, 1)
```

@@

(ref:both-meth1) ...

```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

(ref:div-repl-meth1) The figure shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))

sim_length <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(simlength == sim_length)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " sim. length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2

```{r echo = FALSE, eval = FALSE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

@@

```{r echo = FALSE, eval = FALSE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

@@

@@

## Diversity effects

Recall that the temporal method for finding stable states involves running the simulation for a certain amount of time, termed the "wait time", at a constant level of oxygen diffusivity. At the end of that wait time the state of the system is recorded, and then the oxygen diffusivity is slightly increased or decreased, and the system then simulated again for the duration of the wait time.

The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth5) show the effects of diversity with long to shorter wait times.

(ref:div-temp-meth1) Effects of diversity with wait time of 1e6 hours (same figure as in main report).

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

@@

(ref:div-temp-meth2) Effects of diversity with wait time of 1e5 hours.

```{r div-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth2)', fig.height=7, fig.width=6, fig.align="center"}

@@

(ref:div-temp-meth3) Effects of diversity with wait time of 1e4 hours.

```{r div-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth3)', fig.height=7, fig.width=6, fig.align="center"}

@@

(ref:div-temp-meth4) Effects of diversity with wait time of 1e3 hours.

```{r div-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth4)', fig.height=7, fig.width=6, fig.align="center"}
wait_time <- 1e3
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours.

```{r div-temp-meth5, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth5)', fig.height=7, fig.width=6, fig.align="center"}

@@

## Example of transient dynamics at 1e6 hours

(ref:ss-temp-meth3) ...

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
only_SB_variable[13,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
```

(ref:ss-temp-meth4) ...

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
only_SB_variable[13,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
```

# SB diversity effects

Wait times of 1e5 (Figure \@ref(fig:div-temp-meth2) and 1e4 (Figure \@ref(fig:div-temp-meth4) produce qualitatively and often quantitatively very similar to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)). There is, however, a notable difference when there is variation in only SB, or CB-SB variation treatments with wait time of 1e4 (Figure \@ref(fig:div-temp-meth4)). Here, moderate increases in diversity have the same effect as with wait times of 1e6.

However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition. Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift.

(ref:ss-temp-meth1) Stable state of the system with moderate level of diversity in only SB, and no diversity in the other two groups.

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

only_SB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(PB_var_gmax_s) < 0.0001
  )
only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]

#only_SB_variable$SB_var_gmax_s

fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])

#fig_state_vs_o2diff(only_SB_variable[13,])
```

Suprisingly, when there is just a little more diversity in the SB then the anoxic to oxic transition happens earlier, i.e. there is large decrease in resilience \@ref(fig:ss-temp-meth2).

(ref:ss-temp-meth2)  Stable state of the system with higher than moderate level of diversity in only SB, and no diversity in the other two groups.

```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[14,])
```

@@

(ref:div-stab-multstrain1)  Effects of diversity on positions of tipping points with different numbers of strains.

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

which_strains <- c(2, 3, 6, 9)
which_wait_time<- 1e6
figure_title <- " "

fig_div_vs_o2diff_multistrain(all_stab, which_strains,
                              which_wait_time, figure_title)
```
